### 2024-05-31 2024-5-13/sections/heuristic.tex
section 7.2

\paragraph*{Under approximation}
%
One way of doing the complement operation is to transform $e_1$ into a regular expression that does not contain counting operators. We compute an under-approximation of $e$ by replacing each occurrence of the counting operators in $e_1$, say $(e_2)^{\{m,n\}}$ or $(e_2^{\{n, \infty\}})$, by $e_2^*$. Let us use $e'_1$ denote the resulting regular expression. Note that $e'_1$ does not contain counting operators. Moreover, it is easy to observe that $\Lang(e_1) \subseteq \Lang(e'_1)$. As a result, we have $\Lang(\overline{e'_1}) \subseteq \Lang(\overline{e_1})$. That is, $\overline{e'_1}$ is an under-approximation of $\overline{e_1}$.

@@

@@

The under-approximation is replacing each counting operator in the subregex of complement with a Kleene star operator. The language of the subregex is a superset of the language of it after under-approximation. In sequential, the complement of the subregex is a subset of origin. Note that this approach only works for non-nested complement, which means there is no other complement operators in the complement. For nested complement,  we naively handle the inner complement operators as paper \cite{Denghang2023} and then under-approximate the outer complement operator.
}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

   If each run makes the accepting condition $\alpha'(\myvec{\overline{v}'}/(R\cup\{r\}))$ false, then the negation of the accepting condition $\neg\alpha'(\myvec{\overline{v}'}/(R\cup\{r\}))$ is true. The negation can be rewriten to $(r=1\wedge \alpha)(\myvec{\overline{v}'}/(R\cup\{r\})) = (r=1)(\myvec{\overline{v}'}/(R\cup\{r\}))\wedge \alpha(\myvec{\overline{v}'}/(R\cup\{r\}))$. In our construction, only the transitions teminate at $f$ increase one to the value of $r$, so that the run must end at $f$ to make $r=1$ be true. $\alpha(\myvec{\overline{v}'}/(R\cup\{r\})) = \alpha(\myvec{v'}/R)$ is also need to be true, implying that the run is an accepting run of $\aut$.
\end{proof}

>>>>

\paragraph*{Under-approximation}
%
One way of doing the complement operation is to transform $e_1$ into a regular expression that does not contain counting operators. We compute an under-approximation of $e$ by replacing each occurrence of the counting operators in $e_1$, say $(e_2)^{\{m,n\}}$ or $(e_2^{\{n, \infty\}})$, by $e_2^*$. Let us use $e'_1$ denote the resulting regular expression. Note that $e'_1$ does not contain counting operators. Moreover, it is easy to observe that $\Lang(e_1) \subseteq \Lang(e'_1)$. As a result, we have $\Lang(\overline{e'_1}) \subseteq \Lang(\overline{e_1})$. That is, $\overline{e'_1}$ is an under-approximation of $\overline{e_1}$.

@@

\paragraph*{Over-approximation}
For $e = \overline{e_1}$, we utilize the CEFA constructed from $e_1$, say $\aut_{e_1}$, to construct a CEFA $\cB$ of $e$ so that $\Lang(\cB)$ is an over-approximation of $\Lang(e)$. 
Let $\aut_{e_1} = (R, Q, \Sigma, \delta, I, F, \alpha)$. The main idea of the construction is explained as follows: If a string $w$ is not accepted by $\aut_{e_1}$, then either there are no runs of $\aut_{e_1}$ on $w$, or every run of $\aut_{e_1}$ on $w$ stop at a non-final state or enter a final state but do not satisfy the accepting condition $\alpha$. We shall construct a CEFA $\cB$ that accepts when one of these situations occurs. Then $\overline{\Lang(\aut_{e_1})} \subseteq \Lang(\cB)$, that is, $\cB$ is an over-approximation of $e$.

Without loss of generality, we can assume that there are no transitions out of $F$ in $\aut_{e_1}$. If this is not the case, then a new state $q_f$ can be introduced to transform $\aut_{e_1}$ into a CEFA satisfying this constraint, where $q_f$ is the unique accepting state. 
Then we define $\cB= (R \cup \{r'\}, Q \cup \{q_s\}, \Sigma, \delta', I, Q \cup \{q_s\}, \alpha')$, where
\begin{itemize}
  \item $r'$ is a new register not in $R$, 
  \item $q_s$ is a new state not in $Q$,
  \item $\delta'$ comprises the following transitions, 
  \begin{itemize}
    \item $(q, a, q', (\vec{v}, 0))$ such that $(q, a, q', \vec{v}) \in \delta$ and $q' \not \in F$,
%
    \item $(q, a, q_s,(\vec{0}, 0))$ such that there do \emph{not} exist $a$-labeled transitions out of $q$, that is, for every $q'$ and $\vec{v}$, we have $(q, a, q', \vec{v}) \not\in \delta$,
%
    \item $(q, a, q', (\vec{v}, 1))$ such that $(q, a, q', \vec{v}) \in \delta$ and $q' \in F$,
%
    \item $(q_s, a, q_s, (\vec{0}, 0))$ such that $a \in \Sigma$, 
  \end{itemize}
  \item $\alpha'$ is defined as $r' = 1 \rightarrow \neg \alpha$.
\end{itemize}
Intuitively, $q_s$ is a sink state that deals with the situations that there are no runs and $r'$ is a register newly introduced so that the different cases of the non-accepting runs of $\aut_{e_1}$ can be captured by a single accepting condition $\alpha'$.

Note that $\cB$ is a strict over-approximation of $e = \overline{e_1}$ since $\aut_{e_1}$ may be nondeterministic. For instance, if there are two runs of $\aut_{e_1}$ on a string $w$, say one run that ends at a non-final state and another run that ends at a final state and satisfies accepting condition $\alpha$. Then $w \in \Lang(\aut_{e_1})$, thus $w \not \in \Lang(\overline{\aut_{e_1}})$. Nevertheless, according to the construction, $w$ is accepted by $\cB$, witnessed by the run of $\aut_{e_1}$ that ends at a non-final state.

@@

The under-approximation is replacing each counting operator in the subregex of complement with a Kleene star operator. The language of the subregex is a superset of the language of it after under-approximation. In sequential, the complement of the subregex is a subset of origin. Note that this approach only works for non-nested complement, which means there is no other complement operators in the complement. For nested complement,  we naively handle the inner complement operators as paper \cite{Denghang2023} and then under-approximate the outer complement operator.

@@

   If each run makes the accepting condition $\alpha'(\myvec{\overline{v}'}/(R\cup\{r\}))$ false, then the negation of the accepting condition $\neg\alpha'(\myvec{\overline{v}'}/(R\cup\{r\}))$ is true. The negation can be rewriten to $(r=1\wedge \alpha)(\myvec{\overline{v}'}/(R\cup\{r\})) = (r=1)(\myvec{\overline{v}'}/(R\cup\{r\}))\wedge \alpha(\myvec{\overline{v}'}/(R\cup\{r\}))$. In our construction, only the transitions teminate at $f$ increase one to the value of $r$, so that the run must end at $f$ to make $r=1$ be true. $\alpha(\myvec{\overline{v}'}/(R\cup\{r\})) = \alpha(\myvec{v'}/R)$ is also need to be true, implying that the run is an accepting run of $\aut$.
\end{proof}
}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
